---
title: "Comparing Linear Models for mtcars dataset"
author: "Klaske Grimmerink"
date: "26 december 2016"
output: ioslides_presentation
---

## Description
This application is build with shiny in R. In this application the user can compare 3 different linear regression models with one input variable to predict the miles per gallon of a vehicle. The dataset mtcars is used.


## Input
The user can choose the input variable for each model. This is done by the function "radioButtons" of the shiny package. With this function only 1 input variable can be selected.
```{r, eval=FALSE}
radioButtons("variable1", 
             "What variable would you like to see in model 1?", 
                       c("Cylinders" = "cyl",
                         "Transmission" = "am",
                         "Gears" = "gear",
                         "Displacement"="disp",
                         "Horsepower"="hp",
                         "Weight"="wt",
                         "1/4 mile time"="qsec"))
```
## Output
The output shows the coefficients of the linear model predicting the miles per gallon (mpg) for the chosen input variable. Also the p-values and the R-squared value are shown. The output for the 3 models are on the same page, so the results can be compared.


## Example
If the user selects the Cylinders as input variable (cyl) for model 1, this is the ouput that is given for this model:
```{r, echo=TRUE, message=FALSE, warning=FALSE}
model1<-lm(mpg~cyl,data=mtcars)
summary(model1)$coef
summary(model1)$r.squared

```
